On the Galaxy Size--Halo Connection

### 2017-08-30 paper/galsize_paper.tex
Migrated figures and captions into latex

@@

>>>>

\section{Data and Simulations}
\label{sec:data}

\subsection{Galaxy Sample}
\label{subsec:galaxydata}

\subsection{Clustering Measurements}
\label{subsec:clusteringmeasurements}

\subsection{Baseline Mock Catalog}
\label{subsec:baselinemock}

\section{Galaxy Profile Model}
\label{sec:model}

\section{Results}
\label{sec:results}

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
\caption{
{\bf One-point data used to fit the fiducial model.}
Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}. Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.14=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations. 
}
\label{fig:scatter_plot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
\caption{
{\bf Two-point clustering data used to validate the fiducial model.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}. We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass. The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels. The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}). 
}
\label{fig:scatter_plot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
\caption{
{\bf Clustering provides tight constraints on the relative sizes of centrals and satellites.} 
Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles. The successful prediction of our fiducial model, in which satellite galaxies neither contract nor puff up after infall, places tight constraints on satellite-specific physical processes, which must be either negligible or conspiratorially produce little-to-no size change after accretion. 
}
\label{fig:satellites}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_spin_size_correlation.pdf}
\includegraphics[width=8cm]{FIGS/central_lensing_spin_size_correlation.pdf}
\caption{
{\bf Clustering and lensing provide no constraining power on the assumption that $\rhalfdisk\propto\halospin.$} 
We compare the predictions between our fiducial model in which sizes are purely stochastic, and an alternative model motivated by \citet{mo_mao_white98} in which central galaxy disk size is maximally correlated with host halo spin at fixed stellar mass \citep[implemented via conditional abundance matching, e.g.,][]{hearin_etal13b}. The tiny differences between the solid and dashed curves imply that conventional large-scale structure measurements cannot even in principle provide compelling evidence pertaining to the assumption that $\rhalfdisk\propto\halospin.$ 
}
\label{fig:halospin_lensing}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

\section{Discussion}
\label{sec:discussion}

\subsection{Relation to Previous Work}
\label{subsec:previouswork}

\section{Conclusion}
\label{sec:conclusion}

\subsection{Summary}
\label{subsec:summary}

@@

\bibliography{galsize_paper}
